Asimilación de distintas observaciones

### 2021-01-19 analysis/chapters/experimento_20181122.Rmd
Cambio varios graficos para unificar estetica

rbindlist(list(no_oficiales, oficiales)) %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_mapa() +
  geom_point(alpha = 0.8, size = 1,
             aes(color = source, shape = source)) +
  scale_shape_manual(name = "Surface\nstations",  breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  "Surface\nstations", values = c("Sfc - Non-official" = "#00695c", 
                                              "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2)))+
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL) +
  theme_minimal() + 
  theme(legend.position = "bottom", legend.justification = "left",
         legend.key.size = unit(0.8, "lines")) +

  plot_spacer() +

  rbindlist(list(ascat, sondeos, aircraf, satwnd)) %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_mapa() +
  geom_point(alpha = 1,
             aes(color = source, shape = source, size = source)) +
  scale_color_manual(values = c("darkorange", "purple", "cyan4", "grey70"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_size_manual(values = c(1.5, 0.7, 0.5, 0.1)) +
  # scale_color_brewer(palette = "Dark2") +
  # khroma::scale_color_vibrant() +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL, y = NULL, color = NULL, shape = NULL, size = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", legend.justification = "left",
        legend.key.size = unit(0.8, "lines")) +

  plot_layout(ncol = 3, widths = c(0.49, 0.02, 0.49)) +
  plot_annotation(tag_levels = "a", tag_suffix = ")")
```

@@

rad %>% 
  .[qc == 0 & iuse == 1] %>% 
  .[, lev := factor(cut_round(peakwt, breaks = seq(0, 1050, 50)))] %>% 
  .[, .(omb = mean(tbc),
        n = .N), by = .(date, lev)] %>% 
  .[lev != 1025] %>% 
  ggplot(aes(date, fct_rev(lev))) +
  geom_tile(aes(fill = n)) +
  scale_fill_viridis_c(trans = scales::log10_trans(), breaks = c(1, 10, 100, 1000, 10000),
                       guide = guide_colourbar(barheight = 18)) +

@@

fread(here("analysis", "data", "derived_data", "uvt_rcrv_box.csv")) %>%   
  .[var %in% c("u", "v") & type %in% c(280, 281, 287, 290)] %>% 
  .[, type.obs := type] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 4, 0.5),
                       limits = c(0, 4),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, 
             labeller = labeller(type.obs = c("280" = "SFCSHP",
                                              "281" = "ADPSFC",
                                              "287" = "ADPSFC\n no pressure",
                                              "290" = "ASCATW"),
                                 var = c("u" = "U wind",
                                         "v" = "V wind" ))) +
  labs(x = "",
       y = "",
       fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

fread(here("analysis", "data", "derived_data", "uvt_rcrv_box.csv")) %>%
  .[var %in% c("t") & type %in% c(180, 181, 187)] %>% 
  .[, type.obs := type] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 5, 0.5),
                       limits = c(0, 5),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, labeller = labeller(type.obs = c("180" = "SFCSHP",
                                                            "181" = "ADPSFC",
                                                            "187" = "ADPSFC\n no pressure"),
                                               var = c("t" = "Temperature"))) +
  labs(x = "",
       y = "",
       fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r rcrv-profile, fig.cap="Profiles of mean and standar deviation of rcrv for sounding and aircraft observations."}
obs.type[fread(here("analysis", "data", "derived_data", "rcrv_uvt_perfil.csv")), on = "type"] %>% 
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(nivel.error, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = factor(code), linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level() +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "u" = "U wind",
                                                "v" = "V wind"))) +
  labs(y = NULL,
       linetype = "",
       color = NULL) +
  theme_minimal() 
```

@@

RCRV %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  setDT() %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  .[, .(value = mean(value, na.rm = TRUE)), by = .(sensor, level, variable)] %>% 
  ggplot(aes(level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sensor, linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  coord_flip() +
  scale_x_level() +
  labs(x = NULL, y = NULL,
       color = NULL, linetype = NULL) +
  theme_minimal()

@@

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "T") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level))) +
  scale_fill_divergent_discretised(name = NULL,
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  labs(subtitle = "Temperature difference (K)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  labs(subtitle = "Specific humidity difference (g/Kg)",
       y = "Pressure level",
       x = NULL) +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s (filled contours) and zonal wind profile for the experiment with more observations."}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-1.6, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL,
                                   limits = c(-1.6, 2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(0, 30, 3), size = 0.3, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1.6, 1.2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-7, 0, 1), size = 0.3, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-7, 0, 1), color = "grey30", skip = 1, stroke = 0.2) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

ana[bottom_top %between% c(1, 10), .(v_mean = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
 # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlGn", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(v_mean))),
                proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10)) +
   geom_text_contour(aes(z = v_mean), size = 4, stroke = 0.05,
                     proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10),
                label.placement = label_placement_n(1)) +
  scale_linetype(guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

ana[bottom_top %between% c(2, 10), .(theta_mean = mean(theta)), 
  by = .(south_north, west_east, date, exp)] %>% 
   .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
 # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = theta_mean, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7,
                    breaks = c(-Inf, seq(290, 314, 2), Inf), limits = c(-Inf, Inf)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "RdYlBu", direction = -1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

mucape %>% 
  .[variable == "mcape"] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  .[cor, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)), 
                    proj = norargentina_lambert, limits = c(500, 6000)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  # geom_contour2(aes(z = cortante),
  #               proj = norargentina_lambert, color = "black", size = 0.4,
  #               breaks = c(10, 25)) +
  geom_point(data = ~.x[cortante >= 10 & is.cross(x, y, skip = 1)], 
             aes(x = lon, y = lat, 
                 alpha = factor(cut_round(cortante, breaks = c(5, 15, 40)))),
             size = 0.00002, shape = 20) +
  scale_alpha_manual(values = c(0.3, 0.7), guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

>>>>

rbindlist(list(no_oficiales, oficiales)) %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_mapa() +
  geom_point(alpha = 0.8, size = 1,
             aes(color = source, shape = source)) +
  scale_shape_manual(name = "Surface\nstations",  breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  "Surface\nstations", values = c("Sfc - Non-official" = "#00695c", 
                                              "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2)))+
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  theme_minimal() + 
  theme(legend.position = "bottom", legend.justification = "left",
         legend.key.size = unit(0.8, "lines")) +

  # plot_spacer() +

  rbindlist(list(ascat, sondeos, aircraf, satwnd)) %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_mapa() +
  geom_point(alpha = 1,
             aes(color = source, shape = source, size = source)) +
  scale_color_manual(values = c("darkorange", "purple", "cyan4", "grey70"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_size_manual(values = c(1.5, 0.7, 0.5, 0.1)) +
  # scale_color_brewer(palette = "Dark2") +
  # khroma::scale_color_vibrant() +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  labs(color = NULL, shape = NULL, size = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", legend.justification = "left",
        legend.key.size = unit(0.8, "lines")) +

  plot_layout(ncol = 3, widths = c(1, 1)) +
  plot_annotation(tag_levels = "a", tag_suffix = ")")
```

@@

rad %>% 
  .[qc == 0 & iuse == 1] %>% 
  .[, lev := factor(cut_round(peakwt, breaks = seq(0, 1050, 50)))] %>% 
  .[, .(omb = mean(tbc),
        n = .N), by = .(date, lev)] %>% 
  .[lev != 1025] %>% 
  ggplot(aes(date, fct_rev(lev))) +
  geom_tile(aes(fill = n)) +
  scale_fill_viridis_c(trans = scales::log10_trans(), breaks = c(1, 10, 100, 1000, 10000),
                       guide = guide_colourbar(barheight = 18,
                                               barwidth = 0.8)) +

@@

fread(here("analysis", "data", "derived_data", "uvt_rcrv_box.csv")) %>%   
  .[var %in% c("u", "v") & type %in% c(280, 281, 287, 290)] %>% 
  .[, type.obs := type] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 4, 0.5),
                       limits = c(0, 4),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, 
             labeller = labeller(type.obs = c("280" = "SFCSHP",
                                              "281" = "ADPSFC",
                                              "287" = "ADPSFC\n no pressure",
                                              "290" = "ASCATW"),
                                 var = c("u" = "U wind",
                                         "v" = "V wind" ))) +
  labs(fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

fread(here("analysis", "data", "derived_data", "uvt_rcrv_box.csv")) %>%
  .[var %in% c("t") & type %in% c(180, 181, 187)] %>% 
  .[, type.obs := type] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 5, 0.5),
                       limits = c(0, 5),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, labeller = labeller(type.obs = c("180" = "SFCSHP",
                                                            "181" = "ADPSFC",
                                                            "187" = "ADPSFC\n no pressure"),
                                               var = c("t" = "Temperature"))) +
  labs(fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r rcrv-profile, fig.cap="Profiles of mean and standar deviation of rcrv for sounding and aircraft observations."}
obs.type[fread(here("analysis", "data", "derived_data", "rcrv_uvt_perfil.csv")), on = "type"] %>% 
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(nivel.error, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = factor(code), linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "u" = "U wind",
                                                "v" = "V wind"))) +
  labs(y = NULL,
       linetype = "",
       color = NULL) +
  theme_minimal() 
```

@@

RCRV %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  setDT() %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  .[, .(value = mean(value, na.rm = TRUE)), by = .(sensor, level, variable)] %>% 
  ggplot(aes(level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sensor, linetype = variable)) +
  scale_color_discrete(labels = toupper) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  coord_flip() +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  labs(x = NULL, y = NULL,
       color = NULL, linetype = NULL) +
  theme_minimal()

@@

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "T") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level))) +
  scale_fill_divergent_discretised(name = NULL,
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  labs(subtitle = "Temperature difference (K)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  # scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  labs(subtitle = "Specific humidity difference (g/Kg)",
       y = NULL,
       x = NULL) +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r U-diff, fig.cap="Zonal wind difference between experiments in m/s (filled contours) and zonal wind profile for the experiment with more observations."}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-1.6, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL,
                                   limits = c(-1.6, 2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(0, 30, 3), size = 0.2, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1, 
                    size = 4, stroke = 0.1) +
  labs(subtitle = "U difference (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1.6, 1.2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-7, 0, 1), size = 0.2, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-7, 0, 1), color = "grey30", skip = 1, 
                    size = 4, stroke = 0.1) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

ana[bottom_top %between% c(1, 10), .(v_mean = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlGn", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(v_mean))),
                proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10)) +
   geom_text_contour(aes(z = v_mean), size = 4, stroke = 0.05,
                     proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10),
                label.placement = label_placement_n(1)) +
  scale_linetype(guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

ana[bottom_top %between% c(2, 10), .(theta_mean = mean(theta)), 
  by = .(south_north, west_east, date, exp)] %>% 
   .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
 # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = theta_mean, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7,
                    breaks = c(-Inf, seq(290, 314, 2), Inf), limits = c(-Inf, Inf)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "RdYlBu", direction = -1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

mucape %>% 
  .[variable == "mcape"] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  .[cor, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)), 
                    proj = norargentina_lambert, limits = c(500, 6000)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  # geom_contour2(aes(z = cortante),
  #               proj = norargentina_lambert, color = "black", size = 0.4,
  #               breaks = c(10, 25)) +
  geom_point(data = ~.x[cortante >= 10 & is.cross(x, y, skip = 1)], 
             aes(x = lon, y = lat, 
                 alpha = factor(cut_round(cortante, breaks = c(5, 15, 40)))),
             size = 0.00002, shape = 20) +
  scale_alpha_manual(values = c(0.3, 0.7), guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +
